---
name: Aubrey Scown </br>
sn: 62071873

# Question 1

## Part 1
```{r}
sensordata <- read.csv("sensor.csv",
                       header = TRUE, sep = ",")

sensordata$value <- as.numeric(sensordata$value)

head(sensordata, 10)
```

## Part 2
```{r}
sensors_clean <- sensordata

sensors_clean <- subset(sensors_clean, value >= 0 & value <= 100)

tail(sensors_clean)
```

## Part 3
```{r}
data_summary <- list(minread = min(as.numeric(sensors_clean$value)),
  meanread = mean(sensors_clean$value),
  rangeread = range(sensors_clean$value),
  maxcleanread = max(sensors_clean$value),
  s1_s2_readcount = length(sensordata$siteid[lapply(sensordata$siteid, length) == 1  
            | lapply(sensordata$siteid, length) == 2]))

tail(data_summary,5)
```

## Part 4
```{r}
sensorvalues <- as.numeric(sensors_clean$value)

hist(sensorvalues,
main = "Histogram of values",
xlab = "Values")

boxplot(value~sensorid,
data = sensors_clean,
main = "Sensor values by sensor")
```

# Question 2
- Null Hypothesis:
  - It is inconclusive whether or not the mean value of all sensor readings is less than 45
- Alternative Hypothesis:
  - The mean value of all sensor readings is less than 45.
  
```{r}
t.test(sensorvalues,
alternative = "less",
mu = 45)
```

The null hypothesis is rejected, there is sufficient evidence to conclude that the mean of cleaned sensor readings is below 54.

# Question 3
- Null Hypothesis:
  - There is no statistically significant difference between the values observed at site 1 and 2
- Alternative Hypothesis:
  - There is a statistically significant difference between the values observed at site 1 and 2
  
```{r}
s1_s2_sensors <- subset(sensors_clean, siteid == 1 | siteid == 2)

t.test(value ~ siteid, 
data = s1_s2_sensors)
```

The null hypothesis is rejected, there is sufficient evidence to conclude that there is a difference between the values observed at sites 1 and 2

# Question 4
```{r}
advertising <- read.csv("advertising.csv", 
                        header = TRUE, sep = ",")
                        
tail(advertising, 15)

plot(advertising$Radio, advertising$Sales)
plot(advertising$Newspaper, advertising$Sales)
plot(advertising$TV, advertising$Sales)

tvsales_lm <- lm(Sales ~ TV, advertising)

summary(tvsales_lm)

abline(tvsales_lm, col="red")
```